bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
moving datsets

---
title: '\bf Brother, can you spare a manufacturing job? White Voters\' reaction to Deindustrialization'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

national_ts <- read_xlsx("../data/National_Data_TS.xlsx")

@@

# load voting data
library(data.table)
voting <- fread("..\\data\\voting data.csv")

>>>>

---
title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

national_ts <- read_xlsx("../National_Data_TS.xlsx")

@@

# load voting data
library(data.table)
voting <- fread("..\\voting data.csv")
